Concurrent Programming with Harmony

### 2020-08-13 book/paper.tex
Latest

>>>>

\section{Dynamic Allocation}

\begin{figure}
\begin{code}
\harmonysource{stacktest}
\end{code}
\caption{\harmonylink{code/stacktest.hny} Testing a stack implementation.}
\label{fig:stacktest}
\end{figure}

\begin{figure}
\begin{code}
\harmonysource{stack1}
\end{code}
\caption{\harmonylink{code/stack1.hny} Stack implemented using a dynamically updated list.}
\label{fig:stack1}
\end{figure}

\begin{figure}
\begin{code}
\harmonysource{stack2}
\end{code}
\caption{\harmonylink{code/stack2.hny} Stack implemented using static lists.}
\label{fig:stack2}
\end{figure}

\begin{figure}
\begin{code}
\harmonysource{stack3}
\end{code}
\caption{\harmonylink{code/stack3.hny} Stack implemented using a recursive tuple data structure.}
\label{fig:stack3}
\end{figure}

\begin{figure}
\begin{code}
\harmonysource{stack4}
\end{code}
\caption{\harmonylink{code/stack4.hny} Stack implemented using a linked list.}
\label{fig:stack4}
\end{figure}

Harmony supports various options for dynamic allocation.
By way of example, consider a stack.
\autoref{fig:stacktest} presents a test program for a stack.
We present four different stack implementations to illustrate
options for dynamic allocation:
\begin{enumerate}
\item[] \autoref{fig:stack1} uses a single list to represent the
stack.  It is updated to perform \texttt{push} and \texttt{pop} operations;
\item[] \autoref{fig:stack2} also uses a list but, instead of updating
the list, it replaces the list with a new one for each operation;
\item[] \autoref{fig:stack3} represents a stack as a recursively nested tuple
$(v, f)$, where $v$ is the element on top of the stack and $r$ is a stack
that is the remainder;
\item[] \autoref{fig:stack4} implements a stack as a linked list with nodes
allocated using the \texttt{alloc} module.
\end{enumerate}

While the last option is the most versatile (it allows cyclic
data structures), Harmony does not support garbage collection
for memory allocated this way and so allocated memory that is no
longer in use must be explicitly released using \texttt{free}.
